Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-06-25 ms.tex
captions for scatter plots illustrating low-order corrections

\begin{figure}
\begin{center}
\epsfig{file=dipole_all_100.eps, width=3.4in}
\caption{\label{fig:dip}  Scatter plots of \PLANCK~143, 217, 353, and 545 GHz 
versus \PLANCK~857 GHz. Left: before correcting for offset and residual Solar 
dipole. Right: after correcting or the best-fit offset and dipole amplitude, as
described in $\S$\ref{sec:zp}. The dashed red line shows the best-fit linear 
relationship in each case.}
\end{center}
\end{figure}

\begin{figure*}
\begin{center}
\epsfig{file=harm_100.eps, width=6.5in}
\caption{\label{fig:harm} Summary of low-order corrections at 100 GHz.}
\end{center}
\end{figure*}

>>>>

\begin{figure}
\begin{center}
\epsfig{file=dipole_all_100.eps, width=3.4in}
\caption{\label{fig:dip}  Scatter plots of \PLANCK~100, 143, 217, 353, and 545 
GHz versus \PLANCK~857 GHz. Left: before applying zero-level offsets and 
additional low-order corrections. Right: after correcting for the best-fit 
offset and residual Solar dipole (143-545 GHz). 100 GHz is shown after applying
the spherical harmonic correction of Equation \ref{equ:harm}. The dashed red 
line shows the best-fit linear relationship in all cases.}
\end{center}
\end{figure}

\begin{figure*}
\begin{center}
\epsfig{file=harm_100.eps, width=6.5in}
\caption{\label{fig:harm} Summary of low-order corrections at 100 GHz. Left: 
prior to our low-order corrections, a $\sim$17$\mu$K zero-level offset is 
present and strong low-order problems reduce the linearity of the 100 GHz 
scatter versus 857 GHz. Center: scatter plot versus 857 GHz after applying the 
best-fit offset and residual Solar dipole corrections derived with Equation 
\ref{equ:dip} to \PLANCK~100 GHz. The correlation is strengthened, but remains
far less tight than for 143-545 GHz (see Figure \ref{fig:dip}, top four rows, 
right column). Right: after applying the spherical harmonic correction of
Equation \ref{equ:harm} to \PLANCK~100 GHz, the correlation versus 857 GHz is 
far more tightly linear than following the dipole correction.}
\end{center}
\end{figure*}
